
%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------

\EntryTitle{Education.}

\NewEntry{2011-2012}{Universidad de Zaragoza \& UPV/EHU.}

\Description{\MarginText{Computational Mathematics (M.S.)}\textbf{Mathematical Modeling and Numerical Methods in Physics and Engineering.}\newline
Thesis: \textit{CUDA implementation of integration rules within an hp-Finite Element code.}\newline
I learnt how to look for scientific publications, understand them, and rapidly implement code from the papers information.
\begin{itemize}
\item[$\cdotp$] Data mining, neuronal networks, applied statistics, and optimization.
\item[$\cdotp$] Deep formation in Finite Element Modeling.
\end{itemize}
European Official Master, 60 ects credits.\newline
Advisors: Prof.~David \textsc{Pardo}  \ \ $\&$ \ \  Prof.~Ricardo \textsc{Celorrio}\newline
Contact: \href{mailto:\emailDavidPardo}{\emailDavidPardo} \  $\cdotp$\ \ \href{mailto:\emailRicardoCelorrio}{\emailRicardoCelorrio}}

%------------------------------------------------

\NewEntry{2001-2010}{Universidad de Zaragoza.}

\Description{\MarginText{Physics (B.S.)}\textbf{Theoretical Physics Specialization}\ \ $\cdotp$\ \ Science Faculty Zaragoza University.
\begin{itemize}
\item[$\cdotp$\ ] I acquired a deep mathematical knowledge: Differential equation, mathematical models, non linear dynamical equations. 
\item[$\cdotp$\ ] I learnt to: (a) study and analyze different physical phenomena, and the corresponding governing laws, (b); to experiment with the properties of matter and sources or energy, (c); develop IT and industrial applications.
\end{itemize}}

%------------------------------------------------

\NewEntry{2007-2008}{Telecom Saint-Etienne.}

\Description{\MarginText{Exchange Program}\textbf{Erasmus Exchange Program}\ \ $\cdotp$\ \ Saint-Etienne (France).\newline
Throughout this program I had telecom engineer formation: guide of waves, antennas, optical fibers. \newline
{\href{\webUnivTelecoSEtienne}{T\'el\'ecom Saint-Etienne}}
\& {\href{\webUnivSEtienne}{Univerti\'e Jean Monnet}}.}

%------------------------------------------------

\EndCVSection
