
%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2011-2012}{Universidad de Zaragoza \& UPV/EHU.}

\Description{\MarginText{Computational Mathematics (M.S.)}\textbf{Mathematical Modeling and Numerical Methods in Physics and Engineering.}\newline \vspace{-0.5em} \newline 
Thesis: \textit{CUDA implementation of integration rules within an hp-Finite Element code.}\newline \vspace{-0.5em} \newline
I enrolled in this Master to obtain a deep formation on applied mathematics. The master course aims to develop different skills, such as data mining, neuronal networks, applied statistics, and optimization. It is remarkable, the fact that this work forced me to learn how to look for scientific publications and been able to study, understand and rapidly implement the code from the papers information.\newline
With my thesis project, I have obtained a deep formation in Finite Element Modeling. Under David Pardo \& Ricardo Celorrio's direction. My master thesis was an implementation of a FEM integration problem using CUDA technology. With this work, I acquired the necessary skills to develop FEM simulation software.\newline
The master course it is oriented form an applied mathematical point of view, and it is supported by several enterprises where the more outlined are DEIMOS-SPACE, and GAMESA.\newline
European Official Master, 60 ects credits.\newline
Advisors: Prof.~David \textsc{Pardo}  \ \ $\&$ \ \  Prof.~Ricardo \textsc{Celorrio}\newline
Contact: \href{mailto:\emailDavidPardo}{\emailDavidPardo} \ \ $\cdotp$\ \ \href{mailto:\emailRicardoCelorrio}{\emailRicardoCelorrio}}

%------------------------------------------------

\NewEntry{2001-2010}{Universidad de Zaragoza.}

\Description{\MarginText{Physics (B.S.)}\textbf{Theoretical Physics Specialization}\ \ $\cdotp$\ \ Science Faculty Zaragoza University.\newline
I learnt to simulate physical systems in C \& C++, including Monte-Carlo simulation methods, and FEM simulation methods, differential equation mathematical models, non linear dynamical equations. Particle physics, nuclear physics, radiation protection and dosimetry, statistical behavior of atoms and molecules, thermodynamic, magnetism, laser, optics, solid state physics, quantum mechanics.\newline
I learnt to: (a) study and analyze different physical phenomena, and the corresponding governing laws, (b); to experiment with the properties of matter and sources or energy, (c); develop IT and industrial applications.}

%------------------------------------------------

\NewEntry{2007-2008}{Telecom Saint-Etienne.}

\Description{\MarginText{Exchange Program}\textbf{Erasmus Exchange Program}\ \ $\cdotp$\ \ Saint-Etienne (France).\newline
This year my formation was the correspondent to a course in the {\href{\webUnivTelecoSEtienne}{T\'el\'ecom Saint-Etienne}}
\& {\href{\webUnivSEtienne}{Univerti\'e Jean Monnet}}: guide of waves, antennas, optical fibers.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections
