
%-------------------------------------------------------------------------------
% OTHER INFORMATION
%-------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{\MarginText{Awards \& Recommendation Letters}2012\ \ $\cdotp$\ \ \href{\webRecommendationLetterHolman}{Recommendation Letter,} from \href{mailto:\emailDavidHolman}{David Holman}, for my job at XFlow-CFD.}

\vspace{-0.8em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2012\ \ $\cdotp$\ \ M.S. Thesis: \textit{CUDA implementation of integration rules within an hp-Finite Element code}, qualification 9.6 over 10. }

\vspace{-0.8em}
\Description{2012\ \ $\cdotp$\ \ \href{\webRecommendationLetterPardo}{Recommendation Letter} from \href{mailto:\emailDavidPardo}{David Pardo} , for my work developing a FEM integration method in CUDA.}

\vspace{-0.8em}
\Description{2012\ \ $\cdotp$\ \ \href{\webRecommendationLetterTbSolutons}{Recommendation Letter} from my project manager at Tb-Solutions.}

\vspace{-0.8em}
\Description{2012\ \ $\cdotp$\ \ \href{\webRecommendationLetterESEO}{Recommendation Letter.} from professor Alberto Abad, for my work in \href{\webSiteESEO}{ESEO Project}.}
%------------------------------------------------

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{Spanish}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.8em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Full professional communication. (C1)}

\vspace{-0.8em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \ \ Competent communication, non full professional. (B1)}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

\vspace{1em}
\Description{\MarginText{Other qualifications}2015\ \ $\cdotp$\ \ \href{\webSiteToastMaster}{Toast Master international}. Organization focused on the public speech and leadership personal skills development.}

\vspace{-0.8em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{2010\ \ $\cdotp$\ \ Applied course on Advanced Computation.}

\vspace{-0.8em}
\Description{2010\ \ $\cdotp$\ \ Course on Renewable Energies.}

%------------------------------------------------


\Description{\MarginText{Social skills}Along my period at the University of Zaragoza, I was involved in different projects:
% \vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Member of the student representatives.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ I took part on the organization and development of several events in college.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ I was member of \href{\webSiteLEEM}{LEEM} group. Laboratory to Experimentation in Space and Microgravity.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ I was member of APSIDE (Asociaci\'on Para la Promoci\'on Social de la Investigaci\'on y el Desarrollo Espacial) group, in order to ESEO's satellite development.}
}
%----------------------------------------------------------------------------------------
