
%-------------------------------------------------------------------------------
% WORK EXPERIENCE
%-------------------------------------------------------------------------------

% Section header
\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2014--Present}{\textsc{Mathematical Modeling.} --- Houston} %\textsc{TOTAL E\&P USA} --- Houston}

\Description{\MarginText{TOTAL E\&P USA}As a member of the Computational Applied Mathematics, I have develop a code to propagate waves beneath the soil. The method used to compute the wave propagation is Discontinous Galerkin. The current stages of development are:}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Study and understand the literature about Discontinous Galerkin.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Design \& implement, library subroutines, and unitary tests.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Implement forward propagation. Serial code.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Parallelize the serial implementation.}

\vspace{-0.8em}
\Description{Future development milestones.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Implement wave dissipation in boundaries.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Adjoint problem, for inverse wave propagation.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Test scalability in CPU and GPU.}

% This project with TOTAL E\&P is intended to en in October 31st, 2015.
\vspace{-0.8em}
\Description{Reference: Henri \textsc{Calandra}\ \ $\cdotp$\ \ \href{mailto:emailHenriCalandra}{henri.calandra@total.com} }

%------------------------------------------------
\vspace{0.5em}
\NewEntry{2013--2014}{\textsc{Mathematical Software Developer.} --- Madrid}%\textsc{Xflow-CFD}--- Madrid, Spain}

\Description{\MarginText{Xflow-CFD}XFLow is a high end, high efficiency CFD, Computational Fluid Dynamics, software.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Design and developed a new data architecture, this architecture must be very efficient, lightweight and easy to maintain and modify.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ Part of the data structure designed to be used as graphic user interface was developed with Qt library. }

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ I solve several issues related to XFLow graphic user interface (GUI).}

\vspace{-0.8em}
\Description{Reference: David \textsc{Holman}\ \ $\cdotp$\ \ \href{mailto:\emailDavidHolman}{\emailDavidHolman}}

%------------------------------------------------
\vspace{0.5em}
\NewEntry{Jun-Nov 2011}{\textsc{Software Developer.} --- Zaragoza}

\Description{\MarginText{Tb-Solutions}Tb-Solutions was a company dedicated to develop server-client web-application for banks.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ I Developed an Eclipse plug-in which was used to easily develop the new MC-Server, that is an application for online banking.}

\vspace{-0.8em}
\Description{\ \ $\cdotp$\ \ I took part on the development of the application user interface, of MC-Server.}


%------------------------------------------------
\vspace{0.5em}
\NewEntry{ 2009--2010}{\textsc{Fellowship.} --- Zaragoza}

\Description{\MarginText{ESA student project}ESEO's is a micro-satellite, who was completely developed by European Students as part of an ESA ( European Space Agency ) program. I worked in this program inside the Space Mechanical Group, at Zaragoza's University.}

\vspace{-0.8em}
\Description{I took part inside Mission Analysis (MIAS) team. We develop a code implementation to accurately calculate satellite orbit insertion and the subsequent orbit to all the mission.}

\vspace{-0.8em}
\Description{{\href{\webSiteESEO}{ESEO Project}.}
\\ Reference: Julia \textsc{Mar\'in Yaseli de la Parra}\ \ $\cdotp$\ \ \href{mailto:\emailJuliaMarin}{\emailJuliaMarin}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections
