
%-------------------------------------------------------------------------------
% WORK EXPERIENCE
%-------------------------------------------------------------------------------

% Section header
\EntryTitle{Work Experience.}
% \noindent\spacedlowsmallcaps{Work Experience.}\vspace{0.5em}

\NewEntry{2014--Present}{\textsc{TOTAL E\&P USA.} --- Houston, USA.}

\Description{\MarginText{Mathematical Modeling}As a member of the Computational Applied Mathematics, I have develop a code to propagate waves beneath the soil. The particular method I use to compute the wave propagation is Discontinous Galerkin (DG).
\begin{itemize}
\itemWithDot{Study and understand the literature about DG.}
\itemWithDot{Design, implement, and test library.}
\itemWithDot{Implement forward propagation, and parallelize the implementation.}
\end{itemize}
Future development milestones.
\begin{itemize}
\itemWithDot{Implement wave dissipation in boundaries, adjoint problem, for inverse wave propagation.}
\itemWithDot{Test scalability in CPU and GPU.}
\end{itemize}
Reference: Henri \textsc{Calandra}\ \ $\cdotp$\ \ \href{mailto:emailHenriCalandra}{henri.calandra@total.com}}

%------------------------------------------------
\NewEntry{2013--2014}{\textsc{Xflow-CFD.} --- Madrid, Spain.}

\Description{\MarginText{Mathematical Software Developer.}At XFlow-CFD, I performed the indicated assignments. 
\begin{itemize}
\itemWithDot{Developed \& test new HPC propagator features, and code maintenance.}
\itemWithDot{Designed and develop a new, data architecture.}
\itemWithDot{Implemented GUI with Qt for the new data architecture.}
\end{itemize}
XFLow is a high end, high efficiency CFD, Computational Fluid Dynamics, software. Base on lattice Boltzmann methods.

Reference: David \textsc{Holman}\ \ $\cdotp$\ \ \href{mailto:\emailDavidHolman}{\emailDavidHolman}}


%------------------------------------------------
\NewEntry{Jun-Nov 2011}{\textsc{Tb-Solutions.} --- Zaragoza, Spain.}

\Description{\MarginText{Software Developer}I worked in the development of an Eclipse plug-in for the new 5.0 version of their MC-Server, which is an application for online bank.}

%------------------------------------------------
\NewEntry{ 2009--2010}{\textsc{ESA Student Project.} --- Zaragoza, Spain.}

\Description{\MarginText{Fellowship ESEO project.}I implemented a simulation software to compute the satellite orbit injection and the subsequent orbit to all the mission. ESEO is a ESA ( European Space Agency ) project. Completely developed by European Students. I worked in this program inside the Space Mechanical Group, at Zaragoza's University.\newline{\href{\webSiteESEO}{ESEO Project}.}
\\ Reference: Julia \textsc{Mar\'in Yaseli de la Parra}\ \ $\cdotp$\ \ \href{mailto:\emailJuliaMarin}{\emailJuliaMarin}}

%------------------------------------------------

\EndCVSection
